### 2019-03-04 README.Rmd
readme updates

### Methods

@@

The change in BCG policy was associated with reduced incidence of TB in the study population. This was largely driven by reductions in the non-UK born. There was a slight increase in those at school-age, who were UK born.

>>>>

#### Methods

@@

Withdrawing universal vaccination at school-age and targeting BCG vaccination towards high-risk neonates was associated with reduced incidence of TB in England. This was largely driven by reductions in the non-UK born. There was a slight increase in UK born school-age cases.
